---
title: "globaltrends Firms"
format: gfm
---

A Google Trends-Based Measure of Firm Internationalization 

The current version of the **globaltrends Firms** dataset can be accessed:

+ Country-level search score data by firm ([parquet](https://github.com/ha-pu/globaltrends_firms/blob/main/firms_score.parquet))
+ Volume of internationalization data by firm ([xlsx](https://github.com/ha-pu/globaltrends_firms/blob/main/firms_voi.xlsx), [parquet](https://github.com/ha-pu/globaltrends_firms/blob/main/firms_voi.parquet))
+ Degree of internationalization data by firm ([xlsx](https://github.com/ha-pu/globaltrends_firms/blob/main/firms_doi.xlsx), [parquet](https://github.com/ha-pu/globaltrends_firms/blob/main/firms_doi.parquet))

Cite any usage of the **globaltrends Firms** data as: Puhr, H., & Müllner, J.
(2021). Let me Google that for you: Capturing globalization using Google Trends
(SSRN Working Paper 3969013). Available at
[https://www.ssrn.com/abstract=3969013](https://www.ssrn.com/abstract=3969013).

The **globaltrends Firms** data is part of the [globaltrends project](https://github.com/ha-pu/globaltrends).

* Last update of the data: 2025-11-29
* Coverage of the data: 2010-2024

```{r}
#| echo: false
#| warning: false
#| message: false

library(lubridate)
library(nanoparquet)
library(tidyverse)

df_voi <- read_parquet("firms_voi.parquet")
df_doi <- read_parquet("firms_doi.parquet")
```

## Volume of Internationalization

### Average Annual Volume of Internationalization

```{r}
#| label: voi_annual_average
#| echo: false
#| message: false

df_voi %>%
    filter(voi > 0) %>%
    mutate(year = year(date)) %>%
    summarise(
        voi = mean(voi),
        .by = year
    ) %>%
    ggplot(aes(x = year, y = voi)) +
    geom_line() +
    geom_smooth() +
    labs(
        x = NULL,
        y = "Volume of Internationalization"
    ) +
    theme_bw()
```

## Degree of Internationalization

### Average Annual Degree of Internationalization

```{r}
#| label: doi_annual_average
#| echo: false
#| message: false

df_doi %>%
    filter(gini > 0) %>%
    mutate(year = year(date)) %>%
    summarise(
        gini = mean(gini),
        .by = year
    ) %>%
    ggplot(aes(x = year, y = gini)) +
    geom_line() +
    geom_smooth() +
    labs(
        x = NULL,
        y = "Degree of Internationalization",
        caption = "DOI Measured as Inverted Gini Coefficient"
    ) +
    theme_bw()
```
